Advent Of Code 2020

### 2020-12-06 AdvendOfCode2020/draft_post.Rmd
part 2 of day 3 final

```{r}
# read the files as vector of string
input <- read.csv("./day03_input.txt", header = F)[,1]

@@

>>>>

```{r}
# count trees in a trajectory
# receives a int matrix where "1" is a tree and "0" not
# receives a "shift pattern" for each step down
countTreesByShift <- function(shift.pattern, area.map){

  # apply the pattern until the bottom
  for(i in 1:(nrow(area.map)-1)){
    step <- base_pos + shift.pattern
    base_pos <- step
    trajectory <- rbind(trajectory, step)
  }

  # the columns repeat adjusting the bound
  y_coords <- trajectory[,2] %% ncol(area.map)
  y_coords[y_coords==0] <- ncol(area.map)
  trajectory[,2] <- y_coords
  # avoid out of index in the number of rows
  trajectory <- trajectory[trajectory[,1]<=nrow(area.map),]

  # subset the map with trajectory coordinates and sum
  return(sum(int_map[trajectory]))
}

@@

# test the patterns

# part 1
countTreesByShift(c(1,3),int_map)

# part 2
c(1,1,1,3,1,5,1,7,2,1) %>% 
  matrix(ncol=2, byrow = T) %>%
  split(1:nrow(.)) %>% 
  purrr::map_dbl(countTreesByShift, area.map=int_map) %>% 
  prod()
